Codebook

### 2020-01-13 raw_data/positive_results_in_registered_reports_codebook.Rmd
updated codebook and added .tsv version of dataset to comply with Psych-DS

```{r include=FALSE}
library(here)
library(codebook)
library(readxl)
library(rio)
```

```{r prepare_codebook}
codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)

# Read codebook from second sheet in Excel file.
dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")

@@

#Export codebook
rio::export(codebook_data, "positive_results_in_registered_reports_codebook.rds") # to R data structure file

>>>>

```{r include=FALSE}
library(here)
library(codebook)
library(rio)
```

```{r prepare_codebook}
codebook_data <- import("positive_results_in_registered_reports_masterfile_data.xlsx")

# Read codebook from second sheet in Excel file.
dict <- import("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")

@@

#Export codebook
rio::export(codebook_data, "positive_results_in_registered_reports_data.rds") # to R data structure file
